Inequality in socioemotional skills: a cross-cohort comparison

### 2020-02-03 codes/R/paper/seskills_jpube_rev.Rnw
add CFA with single factor

@@

>>>>

<<FA_INV_AUX_1FAC>>=
# robustness checks with 1 factor
@

@@

\begin{landscape}
\begin{table}[ht]
\caption{Measurement invariance fit comparison -- single factor}\label{tab:fit_1f}
\centering\setstretch{1.2} \scriptsize
<<FA_FIT_RES_1F, dependson="FA_FIT", results='asis'>>=
require(xtable)

# MAKE FIT TABLES
fit_1f <- afitab(list(fa.c.1f, fa.tl.1f, fa.tli.1f), 
                 c("Configural", 
                   "Threshold + Loading Inv", 
                   "Thr. + Load. + Intercept Inv")
)

print(xtable(fit_1f,
                    align="L{0cm}L{.22\\textwidth}C{.08\\textwidth}C{.08\\textwidth}C{.06\\textwidth}C{.06\\textwidth}C{.06\\textwidth}C{.06\\textwidth}C{.06\\textwidth}C{.06\\textwidth}C{.07\\textwidth}C{.07\\textwidth}C{.06\\textwidth}C{.06\\textwidth}C{.06\\textwidth}",
                    digits = 4
                    ),
             size="\\footnotesize",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0)),
                              command = c(
                              # header
            "& & \\multicolumn{6}{c}{\\textbf{Absolute fit}} & \\multicolumn{6}{c}{\\textbf{Relative fit}} 
                  \\\\ \\cmidrule(lr){3-8} \\cmidrule(lr){9-14}
            Model & Num. par. & $\\chi^2$ & RMSE & SRMR & MFI & CFI & G-hat & $\\chi^2$ $p$ & \\textDelta RMSE & \\textDelta SRMR &  \\textDelta MFI & \\textDelta CFI & \\textDelta G-hat \\\\ 
& (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12) & (13) \\\\ \\midrule"
                              )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabular", width = "\\textwidth",
             floating = FALSE
)

@
\justify {\scriptsize \emph{Notes}: The table presents fit indices for models of different invariance levels, following \cite{Wu2016a} Col. (1) displays the number of estimated parameters for each model. Col. (2) and (8) present the value of the $\chi^2$ statistic and the pvalue of the test of equality with respect to the configural model. Col. (3)-(7) and (9)-(13) present alternative fit indices (AFIs), in absolute values and differences from the configural model respectively. RMSE = Root mean squared error of approximation; SRMR = standardised root mean residual; MFI = McDonald non-centrality index; CFI = comparative fit index; G-hat = gamma-hat.
\par}
\end{table}
\end{landscape}
